Comparing OTU quality across clustering strategies

### 2021-10-29 exploratory/2021/test-criteria_2021-04.Rmd

## OTU Quality

```{r crit_mcc}
dat %>% 
  ggplot(aes(x = criteria, y = mcc, color = printref)) +
  geom_jitter(alpha = 0.5, width = 0.2) 
```

## Fraction mapped

```{r crit_map}
dat %>% 
  ggplot(aes(x = criteria, y = fraction_mapped, color = printref)) +
  geom_jitter(alpha = 0.5, width = 0.2)
```

## Runtime

```{r crit_runtime}
dat %>% 
  ggplot(aes(x = criteria, y = sec, color = printref)) +
  geom_jitter(alpha = 0.5, width = 0.2)
```

>>>>

```{r crit_facet, fig.dim = c(5, 5)}
dat %>% 
  pivot_longer(c(mcc, fraction_mapped, sec), 
               names_to = "metric") %>% 
  ggplot(aes(x = criteria, y = value, color = printref)) +
  geom_jitter(alpha = 0.5, width = 0.2) +
  scale_color_manual(values = c("darkorange", "cyan4")) +
  facet_wrap("metric", scales = "free", nrow = 3) +
  coord_flip()
```
